title: "Developing Data Products Project 3"
author: "Roger Li"
date: "7/13/2020"
output: ioslides_presentation
---
## R Markdown
This is an data analysis presentaion for the Developing Data Products.In this presentation, I will use the Mtcars dataset in R software. 

The mtcars dataset was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

Source:**Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.**

## Summary Statistics
The summary of variables is shown below: 
```{r sum}
data(mtcars)
summary(mtcars)
```

## Correlation 
```{r cor,results='hide',warning=FALSE}
library(corrplot)
cormax<-cor(mtcars)
```

```{r cor2}
corrplot(cormax, order = "FPC", method = "color", type = "lower", 
     tl.cex = 0.8, tl.col = rgb(0, 0, 0))
```
From the correlation matrix, it seems that MPG is highly correlated with vs, drat and gear varible. 

## Regression Analysis
In this section, we use AIC to find the optimal multi-varible regression to explain the variation in MPG and the result was shown below:
```{r reg,results='hide'}
mdl<-lm(mpg~cyl+disp+hp+drat+wt+qsec+vs+am+gear+carb,mtcars)
mdl<-step(mdl, direction = "both")
```

```{r reg2,echo=TRUE}
summary(mdl)
```

## Shiny App
Another presentation of the result of this analysis is done by using the Shiny App. The corresponsing can be found in the following github link:
    **https://github.com/Rogerli2019/Developing-Data-Products-Project-3.git**
